---
title: "Hw3"
author: "Naor Dalal & Koren Levenbrown"
date: "12/26/2017"
output: github_document
---
##1.A

```{r}
library(igraph)
ga.data <- read.csv('part1/ga_edgelist.csv', header = T)
g <- graph.data.frame(ga.data,directed = F)
plot(g)
```

```{r}
gDerived <- delete.vertices(g , c('adele' , 'chief' , 'susan grey' , 'thatch grey' , 'ellis grey' , 'tucker' , 'bailey' , 'ben'))
plot(gDerived)
```

###i. By Betweenness

```{r}
between <- betweenness(gDerived)
between[which.max(between)]
```

###ii. By closeness

```{r}
close <- closeness(gDerived)
close[which.max(close)]
```

###iii. By Eigenvector

```{r}
eig <- eigen_centrality(gDerived)
eig$vector[which.max(eig$vector)]
```



##1.B

###Girvan-Newman community detection
```{r}
gc <- edge.betweenness.community(g)
gc
```


```{r}
memb <- membership(gc)
memb
```

Plot the graph with unique color for each community accordingly

```{r}
plot(g, vertex.size=7, #vertex.label=NA,
     vertex.color=memb, asp=FALSE)
```


There is 7 communities

```{r}
length(unique(memb))
```


The size of each community

```{r}
t <- as.data.frame(table(memb))
colnames(t) <- c('ID' , 'Size')
t
```

The modularity

```{r}
gc$modularity
```

###walktrap community

```{r}
gc1 <- walktrap.community(g)
gc1
```


```{r}
memb1 <- membership(gc1)
memb1
```

Plot the graph with unique color for each community accordingly

```{r}
plot(g, vertex.size=7, #vertex.label=NA,
     vertex.color=memb1, asp=FALSE)
```


There is 7 communities

```{r}
length(unique(memb1))
```


The size of each community

```{r}
t1 <- as.data.frame(table(memb1))
colnames(t1) <- c('ID' , 'Size')
t1
```

The modularity

```{r}
gc1$modularity
```



##2

```{r}
library(igraph)
library(twitteR)
library(tm)
library(httr)
```

Set twitter keys
```{r}
consumer_key <- "Y0NniYiJCKL7qqbrreh6p9P4F"
consumer_secret <- "yZlDnWZEB20LrrdVPXwTIY6skmuj9N3iljcO3cGvugrwSJlhYu"
access_token <- "945458627669786624-LsmOz4oCzo0lT6UHwSkPv6hT0inP47x"
access_secret <- "2jwReQYUJHFTDAjQhs0y3Yt1v4MAO2zyAddddBXMVJF4N"
```

Set up the OAuth credentials for a twitteR session
```{r}
sig <- setup_twitter_oauth(consumer_key, consumer_secret, access_token, access_secret)
```

##2.A

###Search tweets on bitcoin on english since 01/12/2017

```{r}
tweets <- searchTwitter("#bitcoin", n=200 , lang = "en" , since = "2017-12-01")
```

convert the tweets to dataFrame

```{r}
tweetsDf <- twListToDF(tweets)
summary(tweetsDf)
```

Get users that publish the tweets
```{r}
users <- twListToDF(lookupUsers(tweetsDf$screenName))

```


##2.B
Our vertexes are user's names and the edge between two users means that their account created on the same month

```{r}
library(lubridate)
users1Edge <- c()
users2Edge <- c()

for(i in 1:nrow(users))
{
  for(j in 1:nrow(users))
  {
    user1 <- users[i,]
    user2 <- users[j,]
    user1Month <- month(as.POSIXlt(user1$created, format="%d/%m/%Y"))
    user2Month <- month(as.POSIXlt(user2$created, format="%d/%m/%Y"))
    
    if((user1$screenName != user2$screenName) && user1Month == user2Month)
    {
      users1Edge <- c(users1Edge , user1$screenName)
      users2Edge <- c(users2Edge , user2$screenName)
    }
  }
}

```


##2.C
Create file from users1Edge and users2Edge and read the file to graph

```{r}
res <- cbind(from = users1Edge , to = users2Edge)
write.csv(res , file = "part2/tweets.csv" , row.names = FALSE)
ga.data <- read.csv('part2/tweets.csv', header = T)
g <- graph.data.frame(ga.data,directed = F)
plot(g, vertex.size=7, vertex.label=NA, asp=FALSE)
```


##2.D

###1.A

###i. By Betweenness

```{r}
between <- betweenness(g)
between[which.max(between)]
```

###ii. By closeness

```{r}
close <- closeness(g)
close[which.max(close)]
```

###iii. By Eigenvector

```{r}
eig <- eigen_centrality(g)
eig$vector[which.max(eig$vector)]
```



###1.B

###Girvan-Newman community detection
```{r}
gc <- edge.betweenness.community(g)
gc
```


```{r}
memb <- membership(gc)
memb
```

Plot the graph with unique color for each community accordingly

```{r}
plot(g, vertex.size=7, #vertex.label=NA,
     vertex.color=memb, asp=FALSE)
```


There is 12 communities

```{r}
length(unique(memb))
```


The size of each community

```{r}
t <- as.data.frame(table(memb))
colnames(t) <- c('ID' , 'Size')
t
```

The modularity

```{r}
gc$modularity
```

###walktrap community

```{r}
gc1 <- walktrap.community(g)
gc1
```


```{r}
memb1 <- membership(gc1)
memb1
```

Plot the graph with unique color for each community accordingly

```{r}
plot(g, vertex.size=7, #vertex.label=NA,
     vertex.color=memb1, asp=FALSE)
```


There is 12 communities

```{r}
length(unique(memb1))
```


The size of each community

```{r}
t1 <- as.data.frame(table(memb1))
colnames(t1) <- c('ID' , 'Size')
t1
```

The modularity

```{r}
gc1$modularity
```

